A Kochen-Specker system has at least 22 vectors

### 2015-05-11 paper/main.tex
paper: /010/-colored
paper: add count

\begin{proposition}\label{prop:ks-triconn}
    A minimal Kochen-Specker graph is edge-triconnected.
    That is: removing any two edges keeps the graph connected.
\end{proposition}
Again, we need some preparation.  First, we generalize
the notion of fixed color.
\begin{definition}
   Given a graph~$G$ together with selected vertices~$v_1, \ldots, v_n \in G$.
   The \keyword{type~$t$ of~$(v_1,\ldots,v_n)$ (in~$G$)}
   is the set of all possible ways $\{v_1, \ldots, v_n\}$ can be colored.
        That is:
\begin{equation*}
  t = \bigl\{ (c(v_1), \ldots, c(v_n)); \ 
        c \colon G \to \{0,1\},\ 
        \text{$c$ is a $010$-coloring of~$G$} \bigr\}
\end{equation*}
    A type of~$n$ vertices is
    called an~\keyword{$n$-type}.
\end{definition}

@@

    All these 12339 graphs are not embeddable.
    See Computation~\ref{comp:unemb20}.
\end{comp}
The computation was distributed on approximately 300 CPU cores
and took roughly three months.
It was executed as follows.
We enumerated all squarefree graphs with minimal vertex
order 3 on less than or equal~$21$ vertices,
using the~\texttt{geng} util of the nauty software package,
which uses the isomorphism-free exhaustive generation
method of McKay\cite{geng}.
The output of~\texttt{geng}, we passed through
a custom heuristic backtracker written in~C++
to decide 010-colorability of these graphs.

>>>>

\begin{proposition}\label{prop:ks-triconn}
    A minimal Kochen-Specker graph is edge-triconnected.
    That is: removing any two edges keeps the graph connected.
\end{proposition}
Again, we need some preparation.  First, we generalize
the notion of fixed color.
\begin{definition}
   Given a graph~$G$ together with selected vertices~$v_1, \ldots, v_n \in G$.
   The \keyword{type~$t$ of~$(v_1,\ldots,v_n)$ (in~$G$)}
   is the set of all possible ways $\{v_1, \ldots, v_n\}$ can be $010$-colored.
        That is:
\begin{equation*}
  t = \bigl\{ (c(v_1), \ldots, c(v_n)); \ 
        c \colon G \to \{0,1\},\ 
        \text{$c$ is a $010$-coloring of~$G$} \bigr\}
\end{equation*}
    A type of~$n$ vertices is
    called an~\keyword{$n$-type}.
\end{definition}

@@

    All these 12339 graphs are not embeddable.
    See Computation~\ref{comp:unemb20}.
\end{comp}
The computation was distributed on approximately 300 CPU cores
and took roughly three months.
It was executed as follows.
We enumerated all squarefree graphs with minimal vertex
order 3 on less than or equal~$21$ vertices\footnote{%
On 21 vertices, we found 24,888,945,914,244 such graphs.},
using the~\texttt{geng} util of the nauty software package,
which uses the isomorphism-free exhaustive generation
method of McKay\cite{geng}.
The output of~\texttt{geng}, we passed through
a custom heuristic backtracker written in~C++
to decide 010-colorability of these graphs.
